\documentclass{article}
\usepackage{float}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{float}
\usepackage{enumitem}

\title{Development Plan\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Date1 & Name(s) & Description of changes\\
Date2 & Name(s) & Description of changes\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

\newpage{}

\noindent This document outlines our team member expectations, guidelines and expected project plan from technology to meeting format. Cow-puter Vision aims to streamline Canadian farmers' day-to-day tasks with a machine learning solution focused on detecting cow attributes and/or behaviours. 

\section{Confidential Information?}

Our project has confidential information from industry. At the moment, we are waiting to recieve a formal non-disclosure agreement from our industry advisor.

\section{IP to Protect}

Our project involves IP to protect. Our team agrees to sign the "Intellectual Property Guide Acknowledgement". At the moment, we are waiting for guidance from our industry advisor regarding IP documentation

\section{Copyright License}

Our team will not assign a copyright license to the repository at the moment. We will follow licensing requirements as specified by our industry advisor.

\section{Team Meeting Plan}
\textbf{Team meetings} will be held once a week on Mondays at 6pm for an hour to share general updates and to delegate tasks. The meeting will be moved to an open lecture time slot if and only if a lecture is not scheduled on a given week and the team is available during that lecture slot. Meetings will be held online on Teams if they are scheduled outside of lecture time. Meetings will be held in person if they are scheduled during lecture time. Whether a meeting is scheduled on Monday at 6pm or during a lecture slot will be confirmed on the Sunday before the week starts.

\vspace{1em}

\noindent \textbf{Additional meetings} may be scheduled on demand during empty lecture slots or during a time when everyone required for said meeting is available.

\vspace{1em}

\noindent \textbf{Weekly meetings with the industry advisor} will be held virtually on Teams weekly on an agreed upon day and time. 

\vspace{1em}

\noindent \textbf{Meeting Format:}
The Notetaker will share the meeting agenda in the Teams channel the day before the meeting is scheduled for. The Backlog Manager will create a GitHub Issue for the meeting. Team meetings will be led by the Meeting Chair and will follow the agenda template provided below:
\begin{itemize}
  \item \textbf{10-15 minutes:} Individual updates on personal tasks (updating kanban board on GitHub)
  \item \textbf{40 minutes:} Group work (project deliverables/decision making/brainstorming)
  \item \textbf{5-10 minutes:} Task delegation for the week (updating kanban board on GitHub)
\end{itemize}

\noindent Industry advisor meetings will follow the breakdown provided below:
\begin{itemize}
  \item \textbf{10-15 minutes:} Individual updates on personal tasks and plan for upcoming week
  \item \textbf{30 minutes:} Q\&A with Industry Advisor
\end{itemize}

\section{Team Communication Plan}
Our team's means of communication will primarily comprise of a Microsoft Teams group chat, an iMessage group chat, and GitHub issues. Our Microsoft Teams group chat is suited for discussions about the project.
Some examples of discussions are: someone asking for help on how to resolve an error and someone confirming with team members before 
taking action on an important task. Our iMessage group chat is useful for situations such as:
confirming an in-person meeting's location and someone sending a text to indicate that they will be arriving a couple of minutes late to the
in-person meeting. Our iMessage group chat has also allowed us to exchange phone numbers with each other.
Having each others' phone numbers is useful for one to one communication situations. Some examples of these situations are:
calling someone to ask if their assigned task is done and 
if someone has an assigned task that depends on another team member's work, it might text or call the team member to get clarity and understand the team member's work.
Our team will not be using email to communicate with each other. Email will only be used to communicate with our project supervisor, other project
stakeholders, the course instructor, and our assigned TA. That being said, we still have each others' emails. GitHub issues will primarily be used for putting meeting agendas for meetings,
summarizing a meeting's key points, and indicating the people that attended the meeting. Moreover, since
lectures are also considered as meetings, GitHub issues will be created for lectures. For a lecture, the issue would
summarize the lecture's key points and indicate the people that attended the lecture.


\section{Team Member Roles}

For the remainder of this project, we will work collaboratively as a team following assumed roles to develop the Cow-puter Vision project. These defined roles may have different assignees at different stages of the project, as team members may wish to rotate between the roles.
The table below contains a list of all the roles and respective descriptions that are believed to be essential to ensure successful collaboration and achievement of the project goals:

\subsection{Non-technical Roles}
\begin{table}[ht]
\centering
\caption{Non-technical roles and descriptions}
\label{tab:non-technical-roles}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Role} & \textbf{Description} \\
\midrule

Team Liaison & Acts as the main point of contact between the team and supervisors and stakeholders.  \\ \\
Notetaker & Records meeting minutes, lecture notes, and sets agenda. \\ \\
Meeting Chair & Facilitates team discussions, ensuring that the team remains focused on the meeting agenda without going off on tangents. \\ \\
Backlog Manager & Creates, tracks, and assigns project-related GitHub issues based on deliverable sections and sets their priority based on deadlines and business value.\\ \\
\bottomrule
\end{tabularx}
\end{table}

\noindent\textbf{Important Note:} Backlog Manager is not soley responsible for creating GitHub issues, and is only responsible for creating issues based on the deliverable sections. Example: Backlog
Manager is responsible for creating issues such as "Complete section 1.1" and "Review section 1.1". Issues involving very specific tasks, 
that are not clearly outlined or sectioned on deliverable templates, such as fixing specific bugs, fall under the responsibility of 
the team member(s) who encounters the issue or task to begin with.\\

\subsection{Technical Roles}
\begin{table}[H]
\centering
\caption{Technical roles and descriptions}
\label{tab:technical-roles}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Role} & \textbf{Description} \\
\midrule

Computer Vision \& ML Engineer & Responsible for leading design and development of the ML model, including model training and evaluation of the computer vision models using the preprocessed cow data, as well as ensuring that the model achieves satisfactory performance.\\ \\
Data Pipeline Engineer &  Responsible for leading the collection, organization and preprocessing of the raw image/video data, ensuring it is properly labeled and cleaned, and preparing it into standardized datasets ready for model training and evaluation.\\ \\
Backend \& Integration Engineer  & Responsible for leading the development of APIs or services that connect the trained model to the frontend, and manages a database to store any necessary data, ensuring smooth communication between components and managing data flow through the system \\ \\
Frontend \& UI/UX Engineer  & Responsible for leading the design and development of interface for farmers to interact with, and ensure that the necessary results are clearly displayed to them. \\ \\
Deployment \& Testing Lead & Responsible for ensuring that the model deploys to the target environment, testing and validating the accuracy and reliability of the system, running end-to-end tests, and fixing integration issues\\ \\
\bottomrule
\end{tabularx}
\end{table}


\section{Workflow Plan}

GitHub will be used to manage the team’s codebase and contributions. The main branch will house finished code that the team has worked on together and agreed needs no further editing, pending a design change or feedback.\\  

New Branches will be created to track work done on a feature, issue, or task. The branch name will follow the following format: \\ 

\textless Issue\textunderscore Name\textgreater-\textless AuthorInitials \textgreater-\textless SecondaryAuthorInitials\textgreater \\

For example:  \\

Add\textunderscore Menu\textunderscore Options-CN \\

When a feature is ready to be merged, a merge request for the feature branch into main will be created. It must be reviewed by at least one separate team member, to the author’s discretion based on availability and/or knowledge of the topic. Once the review has passed, the branch may be merged into main and the team notified to pull recent changes.  \\

GitHub issues will be used to track meeting minutes, lecture notes, meeting agendas, and planned features to implement. Features will be assigned to the developer, and meeting minutes/agendas/lecture notes will be assigned to the attendees for record. GitHub project boards will be used to track features and fixes planned to be implemented. The team will use a Kanban Board to track the implementation status of the GitHub Issues mentioned above.  The team will rotate through who’s responsibility it is to update the Kanban Board and Issues.  \\

Formal feedback on a teammate’s code should be done during the review phase of a merge request, or during development. Feedback done during review may be in the form of comments on a merge request, or in person. If feedback is given after a branch is merged, the team must discuss together what must be changed, and if necessary, a new branch may be opened and immediately approved as a hotfix branch. If the changes are more elaborate, a new branch must be opened and follow usual branch review and merge procedures.  \\

\section{Project Decomposition and Scheduling}

\subsection{Github Projects}
Github Projects will be used for project management of tasks. The group will use the Kanban board feature on Github projects to assign tasks. Tasks will be categorized under milestones and will be assigned to individual team members. They can take on one of three states: 
\begin{itemize}
  \item \underline{To do:} Tasks that are backlogged and are not currently being worked on. 
  \item \underline{In progress:} Tasks that are currently being worked on.
  \item \underline{Done:} Completed tasks that have been reviewed by another member and approved.
\end{itemize}

\noindent Github Issues will also be used to track team meeting agendas, supervisor meetings, lecture notes, TA meetings, and peer reviews. The link to the Github repository where the project can be found will be linked \underline{\href{https://github.com/rosachen3/Cowgnition/tree/main}{here}}.

\subsection{Schedule}
The project will follow the major deadlines outlined below. Each task will have subtasks assigned as the semester progresses. These can be tracked in the Github Projects Kanban Board.

\begin{table}[H]

\centering
\caption{List of Milestone Deadlines}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Milestone} & \textbf{Due Date} \\
\hline
Team formation and Project Selection & September 15 \\
\hline
Problem Statement, Goals and Development Plan & September 22 \\
\hline
SRS + HA & October 6 \\
\hline
V\&V Plan Revision 0 & October 27 \\
\hline
Design Documentation Revision -1 & November 10 \\
\hline
Proof of Concept Demonstration & November 17 \\
\hline
Design Document Revision 0 & January 19 \\
\hline
Revision 0 Presentation & February 2 \\
\hline
V and V Report and Extras Revision 0 & March 9 \\
\hline
Final Demonstration (Revision 1) & March 23 \\
\hline
Final Documentation (Revision 1) & April 6 \\
\hline
EXPO Demonstration & TBD \\
\hline
\end{tabularx}
\end{table}

\section{Proof of Concept Demonstration Plan}

CATTLEytics will be providing video training data from local partnering farmers. The videos will be used to analyze and categorize cows based on behaviours and physical traits.  

\vspace{1em}

\noindent The following risks have been identified to evaluate the feasibility of the project. 

\vspace{1em}

\begin{itemize}
  \item \noindent \textbf{Farmer Partnerships:} CATTLEytics is a small startup company. Currently, there is no video training data as resources are provided as needed when developing new features. There are local farmers who have agreed to send video data, but there is a risk of delays which could slow down development. 
  \item \noindent \textbf{Data Quality and Quantity:} Machine learning algorithms depend heavily on the data set. There is a risk that the video data collected from farmers will be of low quality or quantity, reducing the accuracy and reliability of the machine learning model. For the Proof of Concept, this risk can be mitigated by using publicly available video data of cows. 
  \item \noindent \textbf{GPU Resources:} The CAS department at McMaster offers departmental resources for machine learning purposes. As these resources are limited, there is a risk that these resources may not be available when the model needs to be trained. A possible risk mitigation strategy is to leverage the use of cloud-based GPU resources to supplement departmental resources if needed.
  \item \noindent \textbf{Environmental Requirements:} Farmers in rural communities may have limited hardware and connectivity. If a system is too resource intensive, farmers may face challenges using the system effectively. For the Proof of Concept, this risk can be mitigated by demonstrating the usage of processing and analyzing collected video data in a controlled environment, without requiring real-time analysis. 
  \item \noindent \textbf{Implementation:} Team members have limited experience with machine learning problems. As a result, researching about existing open-source models and fundamentals may lead to delays. However, the project will be supervised by Luke Schuurman from CATTLEytics who can provide technical advice from a software engineering standpoint. 
  \item \noindent \textbf{Licensing:} Many popular frameworks and pretrained models have licenses that prohibit commercial use. While this may not impact the Proof of Concept, the licenses can become a risk as the project progresses into a commercially available product. This risk can be mitigated by documenting the licenses of all tools and commercially available alternatives.
\end{itemize}

\noindent \textbf{POC Plan:} The Proof of Concept will show that the system is functional and that the risks mentioned can be mitigated. This will ensure that the project can be completed on schedule. 
The demonstration will show that the machine learning model can successfully identify and classify one cow parameter. The demonstration will use a small dataset to validate the system, proving that the model can successfully preprocess and train data using the available GPU resources. The results of the model will be presented in a user-friendly format for farmers to easily access. 

\section{Expected Technology}

This project will have a machine learning aspect, along with a user interface or dashboard, and a data processing pipeline. The technologies below were selected initially, however, there will be changes as the project progresses due to stakeholder constraints and future design choices.

\begin{table}[H]
\caption{Languages and Libraries} \label{TblLanguagesAndLibraries}
\begin{tabularx}{\textwidth}{p{3.5cm}p{7cm}}
\toprule
\textbf{Technology} & \textbf{Explanation}\\
\midrule
Python & Most widely-used language for machine learning and dashboard development.\\
\addlinespace
NumPy, Pandas, Matplotlib & Common libraries used for data manipulation visualization.\\
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[!htbp]
\caption{Machine Learning} \label{TblMachineLearning}
\begin{tabularx}{\textwidth}{p{3.5cm}p{7cm}}
\toprule
\textbf{Technology} & \textbf{Explanation}\\
\midrule
PyTorch, TensorFlow & Widely used frameworks for machine learning.\\
\addlinespace
YOLOv8, Faster R-CNN, DETR & Object detection architectures to be used for custom detectors.\\
\addlinespace
OpenCV & Computer vision library. Includes object detection algorithms.\\
\addlinespace
ImageNet-1000 & Dataset containing 1000 different categories. May be a good starting point for cow detection.\\
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[!htbp]
\caption{Storage and Environment} \label{TblStorageAndEnvironment}
\begin{tabularx}{\textwidth}{p{3cm}p{7.5cm}}
\toprule
\textbf{Technology} & \textbf{Explanation}\\
\midrule
PostgreSQL & To store data on cow behaviour and/or attributes.\\
\addlinespace
Docker & Allows us to build and deploy our application.\\
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[!htbp]
\caption{Development Tools and Testing} \label{TblDevelopmentToolsAndTesting}
\begin{tabularx}{\textwidth}{p{3cm}p{7cm}}
\toprule
\textbf{Technology} & \textbf{Explanation}\\
\midrule
Git & For version control and organization.\\
\addlinespace
GitHub Projects, GitHub Issues & For project tracking and task delegation.\\
\addlinespace
GitHub Actions & May be used for CI/CD pipeline.\\
\addlinespace
Pytest & Python testing framework to be used in our CI/CD pipeline.\\
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[!htbp]
\caption{Front-End} \label{TblFrontEnd}
\begin{tabularx}{\textwidth}{p{3cm}p{7cm}}
\toprule
\textbf{Technology} & \textbf{Explanation}\\
\midrule
Streamlit or React.js & Web-based Front-end options based on the desired level of complexity in our UI.\\
\addlinespace
PyQt/PySide & Option for a desktop standalone app.\\
\bottomrule
\end{tabularx}
\end{table}


\section{Coding Standard}

The team will follow several predetermined standards for branch names, commit messages, and coding. As outlined in Section 7, branch names will follow the following format:  \\

\textless Issue\textunderscore Name\textgreater-\textless AuthorInitials \textgreater-\textless SecondaryAuthorInitials\textgreater \\

For example:  \\

Add\textunderscore Menu\textunderscore Options-CN \\

The team will endeavor to have meaningful and focused commit messages. For maximum readability and cohesion between contributors, the team will follow the standards outlined in 
\href{https://www.conventionalcommits.org/en/v1.0.0/} {Conventional Commits}.  \\

The team is expecting to code in Python and follow the PEP8 coding standard. To ensure that the standard is met, the team will use Ruff as a linter and formatter. Each function is expected to have a block header comment with a brief description of the function’s task, dependencies, inputs and outputs. Variables should be named in camel case.  \\

\newpage{}

\section*{Appendix --- Reflection}

\textbf{Claire Nielsen, Karim Elbasiouni, Rosa Chen}
\begin{enumerate}
    \item \textit{Why is it important to create a development plan prior to starting the project?}\\
    It is important to create a development plan prior to starting the project for several reasons. First, it ensures the team is on the same page about the problem to be solved. Second, the development plan will serve as a guideline, not only for technical practices such as coding standards, but also decision making and collaborating as a team.
    \item \textit{In your opinion, what are the advantages and disadvantages of using CI/CD?}\\
    An easy disadvantage to notice of CI/CD is the overhead it adds to development. Each team member needs to have the environment configured to test their code to ensure it doesn’t conflict with existing code. Since some teammates may not have experience using it, this can add complexity to the codebase. However, its advantages are substantial. Since the project has so many authors working concurrently, CI/CD will minimize conflicts between merged code and new code, testing small chunks of new code against the existing approved codebase. This makes it faster to pinpoint any errors that appear on a merge and discover how to fix it. Overall, it adds a high overhead to the start of development but this time can be made up later due to the help it provides in continuous testing. 
    \item \textit{What disagreements did your group have in this deliverable, if any, and how did you resolve them?}\\
    Since this is the first milestone, the team didn’t have any major disagreements. 
\end{enumerate}

\textbf{Safwan Khan}
\begin{enumerate}
    \item \textit{Why is it important to create a development plan prior to starting the
    project?}\\
    The development plan is a great way to establish our team environment. It helps team members gain a detailed overview of 
    how the team is going to communicate with each other and operate and the expected technologies. Investing time towards this
    will help us better tackle the problem and build a great solution. 

    \item \textit{In your opinion, what are the advantages and disadvantages of using
    CI/CD?}\\
    CI/CD enables consistent integration testing and figuring out if our code works on multiple operating systems. Consistent
    integration testing helps us as a team better understand if our individual contributions still ensure that subsystems and thus the system 
    as a whole are functioning as expected. If our system has bugs, the testing on different operating systems can help us find out if
    the bug is due to a problem in the logic or if it is an operating system specific issue.

    In terms of disadvantages, the main one is that upfront time needs to be spent on both setting up CI/CD for our project and getting comfortable
    with using it.

    \item \textit{What disagreements did your group have in this deliverable, if any,
    and how did you resolve them?}\\
    In this deliverable, one disagreement that we had was setting up a concrete day and time for weekly meetings. At first, as a team,
    none of us could meet weekly at a given day and time. To resolve this, we discussed this problem as a group over a call. Discussing it
    over a call helped us better understand each others' circumstances. Over time, we became more flexible over availabilities. In the end,
    we ended up finding a day and time for our weekly meetings.

\end{enumerate}

\newpage{}

\section*{Appendix --- Team Charter}

\wss{borrows from
\href{https://engineering.up.edu/industry_partnerships/files/team-charter.pdf}
{University of Portland Team Charter}}

\subsection*{External Goals}
Our team hopes to have a positive impact on the targeted users of this product by making their day-to-day tasks easier so they can focus on what matters most on their farms. We also want to gain practical and hands-on experience in the machine learning domain. Artificial Intelligence is a field we all find fascinating, but have yet to explore in depth. Lastly, we look forward to making this a positive learning experience where we can all be proud of the work we produce by the end of the year.

\subsection*{Attendance}

\subsubsection*{Expectations}

\begin{itemize}
  \item \textbf{Weekly Meetings}: With the exception of acceptable excuses and emergencies, team members are expected to attend all meetings. This includes team, supervisor, and TA meetings. Attendance will be logged through the usage of Github Issues. 
  \item \textbf{Punctuality}: It is expected that all team members arrive on time to meetings. If a group member is expected to be more than 15 minutes late or require to leave early for a meeting, the group should be notified through the designated Microsoft Teams or SMS group chat as soon as possible. If a team member needs to miss a meeting, the member must notify the group with a valid reason the day before. They are responsible for reading the meeting minutes, and organizing an alternative time individually or with another team member to catch up on missed work.
\end{itemize}

\subsubsection*{Acceptable Excuse}

\textit{The ‘teammate’ used here to describe the teammate missing a meeting/not completing delegated independent work.} \\

Missing an internal deadline is excusable at the team’s discretion, and due to predetermined justification: 
\begin{itemize}
    \item Family emergencies 
    \item Health complications 
    \item Midterm conflict  \\
\end{itemize} 

Missing an official deadline/deliverable is not acceptable. In the event of a missed deadline, the team will discuss how to fairly handle the situation and move forward on schedule.  \\

In the event of a missed meeting, it is the responsibility of the teammate that missed the meeting to catch up on their own time, using the meeting minutes and/or fellow teammates to ensure they are up to speed. If the meeting was dependent on the missing teammate for a crucial discussion point/work period, the team will schedule an alternate time and 	discuss how to avoid the situation in the future. If a teammate is expecting to have a conflict, this conflict must be communicated by at latest 24 hours before the scheduled meeting time, to allow for the team to decide to proceed with the meeting shorthanded or reschedule. \\

\subsubsection*{In Case of Emergency}

\textit{The ‘teammate’ used here to describe the teammate missing a meeting/not completing delegated independent work.} \\
 
In case of a short notice absence from a meeting, the teammate must notify the rest of the team on MS Teams and/or the iMessage group chat as soon as possible outlining their expected absence and reason for missing the meeting.  \\

In the case of an emergency impeding the completion of independent work, the teammate must notify the rest of the team on MS Teams and/or the iMessage group chat as soon as possible outlining the incomplete work, whether or not they expect to be able to complete it, and explanation. The team can delegate to other members if it impedes an official deadline. If the work violates only an internal deadline and time permits, an extension may be granted to the teammate. Every team member has an unofficial one-time pass for an internal deadline. Multiple offences will lead to a conversation with the team on how to avoid a reoccurrence. 

\subsection*{Accountability and Teamwork}

\subsubsection*{Quality} 
For the quality of preparation for team meetings, our team's expectation is that team members
are aware of what is to be discussed and done in the meeting and work on what is necessary to effectively contribute
in the meeting. For example, if a meeting involves discussion about a milestone document, a reasonable expectation is that team members
go through the document so that they have the necessary context to effectively contribute
in the meeting. In the meeting, if too much time is spent on gathering context, it makes it
difficult to achieve the meeting's goals. Another example is a meeting that involves providing 
individual updates. In this type of meeting, a reasonable expectation is that team members should be able to
clearly give updates about their assigned tasks and explain if they are stuck on something. For the quality of team members' deliverables,
team members should fullfill the purpose and requirements of the deliverables and have clear reasoning behind
their approaches towards their deliverables.


\subsubsection*{Attitude}

We want to create an environment where all ideas are welcome and creative thinking is encouraged. Below is a list of \textbf{team expectations:}

\begin{enumerate}
    \item \textbf{Professionalism:} Team members should deliver high quality work and remain punctual.
    \item \textbf{Respect:} All ideas will be given fair attention and team members will respect opposing ideas.
    \item \textbf{Cooperation:} Everyone on the team is expected to contribute equally to project deliverables and come to meetings prepared.
    \item \textbf{Attitude:} Everyone on the team should maintain a positive, and encouraging attitude to maintain productivity and a low-stress environment.
\end{enumerate}

\noindent In the case that any conflict arises between team members, the following \textbf{conflict resolution plan} will be executed:

\begin{enumerate}
    \item \textbf{Communication:} the first stage of conflict resolution is to communicate the issue one-on-one with the involved team member to define the problem.
    \item \textbf{Find a middle ground:} The involved team members should try to understand each other's perspectives and aim to reach a positive solution.
    \item \textbf{Escalate:} In the case a middle ground cannot be reached, the team will escalate and communicate the issue with Dr. Smith.
\end{enumerate}


\subsubsection*{Stay on Track}

\noindent\textbf{Meeting Deadlines:} The team will employ the use of the official capstone calendar to keep track of dates and deadlines. Each team member is responsible for ensuring that they aware of
upcoming deadlines and potential postponement of these deadlines. Regardless, the team will collectively make an effort to communicate any reminders regarding dates, deadlines,
and any announcements made my the professor through the team's private Microsoft Team's channel. \\

\noindent\textbf{Tracking Progress:} GitHub issues will be created to split milestone tasks to ensure that the volume of work is evenly distributed. Brief progress check-ins will be done at the beginning of every weekly meeting, through which every 
team member is required to share their current progress on their assigned tasks, including any concerns or difficulties that they may have encountered. The team reserves the right to adjust division of responsibilities if a task appears to be
more difficult to complete than expected, or to accomodate for another team member's conflicting schedules, such as in the case when a team member may have external committments or circumstances that other team members do not share. Examples include
conflicting midterm schedules, important medical appointments, etc. \\

\noindent\textbf{Rewards for High Performance:} Team members who perform beyond their expectations will be celebrated in team meetings and given the recognition they rightfully deserve, as well as assigned leadership roles in future milestones that better reflect their
committment to the team. Following the conclusion of the project, the team may pitch in and buy the high performing individual any candy of their choice. Moreover, the team will make a collective request to the professor that the performing individual is given a bonus grade,
though this may or may not be accepted by the professor. \\

\noindent\textbf{Dealing with Unmet Expectations:}
If no extenuating circumstances are present, and a team member is not meeting their workload committments for longer than two weeks or up to the closest milestone, then the following procedure will be followed to address unmet expectations: \\

\begin{enumerate}
  \item Unmet expectations will be addressed briefly as the first item on the agenda of the closest upcoming meeting. If the issue persists, or the team member does not attend the meeting
  proceed to step 2.
  \item The team will have an in-person meeting hosted before, during (if lecture slot is empty), or after lecture to discuss with the team member in question. If the issue persists, or the team member does not attend the meeting
  proceed to step 3.
  \item The team liaison will contact the TA to seek advice on handling the sitaution. If after applying the TA's advice the issue still persists, proceed to step 4.
  \item The team liaison will contact the professor to address the situation.
\end{enumerate}

\noindent\textbf{Consequences for Under-performing:}
The consequences for not meeting the expected workload committment include: 
\begin{itemize}
  \item Negative peer evaluation
  \item Loss of grades
  \item Academic dishonesty punishments
\end{itemize}


\noindent\textbf{Incentives for Meeting Deadlines Early:} Team members who meet deadlines early will be given the option
to have a lighter workload for the next deliverable or milestone. This does not apply for the winter semester,
as the team expects to have a tougher workload around that time period, due to final implementation deadlines. \\

\noindent\textbf{Target Metrics:}
Each team member is responsible to achieve the following metrics to show their contribution:
\begin{itemize}
  \item Attend 100\% of all meetings (except if there is an acceptable excuse)
  \item Confirm review of all documents prior to submission, ensuring adherence to rubric
  \item Contribute to roughly 20\% of the total volume of work, tracked through weekly number of closed issues.
\end{itemize}


\subsubsection*{Team Building}

\begin{itemize}
  \item The team plans on participating in social activities outside of capstone meetings together. These events will be hosted at least once a semester and will occur either on campus or outside of campus (i.e. food, cafes, etc.).  
\end{itemize}  


\subsubsection*{Decision Making} 

Decisions made such as design changes or major changes to projected workflow should be discussed by the entire team and unanimously agreed upon. Decisions made on lower-level workflow (ex. of a function) can be made between assignees of a task if the function behaves as expected in a higher-level design plan. The team should be briefed on these changes.  \\

Should a conflict arise in a team decision, the team should discuss together, ensuring both points are seen and understood. If the conflict remains, the team may choose to seek advisement from the project supervisor and/or our peers (assuming the conflict does not pertain to confidential information). If a resolution is not found, the team may default to a majority vote.   

\end{document}